---
title: "STAT313 Assignment1"
author: "Reuben Brown 57733966"
date: "2023-03-20"
output:
  word_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
# Problem 4

```{r}
# a
x <- ChickWeight$weight
n <- length(x)
alpha <- 0.1
epsilon <- sqrt((1/(2*n)*log(2/alpha)))

est = ecdf(x)
plot(est, do.points=FALSE, col='red')

curve(pmin(est(x)+epsilon, 1), add=TRUE)
curve(pmax(est(x)-epsilon, 0), add=TRUE)
curve(punif(x, min(x), max(x)), add=TRUE)
```
B) We can rule out that the data was sampled from a uniform
distribution as the cdf of the uniform distribution falls
outside of the 95% confidence bands of our empirical distribution
function.

```{r}
# C
ks.test(x, "pnorm")
```
The p-value is smaller than 0.05. This means with 95% certainty we can reject the null hypothesis that the data was sampled from a uniform distribution.

D) I used one-sample ks test so we can directly compare it to a normal distribution rather than using a two-sample test which would compare the data to a randomly generated uniformly distributed sample.


